Search Natural History Specimens in idigbio Database   
-------------------------------------------------------------------------------------------------------------     

### Installing
Please install the following three packages on your computer and library them before running the codes below.   
```
install.packages("ridigbio")
install.packages("knitr")
install.packages("kableExtra")
```   
```{r library, include=FALSE}
library(ridigbio)
library(knitr)
library(kableExtra)
```   


### Function: collection_search   
```
collection_search(Rank, Taxon, Path = NULL, Search_Missing_Taxa = FALSE)
```   
See [README.md](https://github.com/NamikoMachida/Final_Project/blob/master/README.md) for the arguments' details of this function.   


### Examples of function usage   
* Basic specimen search and table visualization   
```{r Basic search, echo=TRUE}
source("./functions.R")
collection_search(rank = "genus", Taxon = c("Acernaspis", "Ananaspis", "Kainops"))
```   



* Specimen search + Species list comparison  
In here, a species-level comparison between downloaded specimen data and a list of species of my interest. My species list is named as mytaxa.txt, which is stored in the same repository. The argument of Search_Missing_Taxa is set as TRUE to find any specimen information that can expand current taxonomic coverage of my data.   
```{r Species comparison, echo=TRUE}
source("./functions.R")
collection_search(rank = "family", Taxon = "Acastidae", Path = "./mytaxa.txt", Search_Missing_Taxa = TRUE)
```   
